---
title: "RLohiya Assignment 11"
author: "Ritesh Lohiya"
date: "November 9, 2018"
output: html_document
---

#                             ASSIGNMENT 8

#           IS 605 FUNDAMENTALS OF COMPUTATIONAL MATHEMATICS

Using the "cars" dataset in R, build a linear model for stopping distance as a function of speed and replicate the analysis of your textbook chapter 3 (visualization, quality evaluation of the model, and residual analysis.)


```{r}
#Lets see summary of the data
summary(cars)
colnames(cars)
nrow(cars)
```

We can see that dataset has 2 columns and 50 rows.

```{r}
#Print the data
cars
```

```{r}
#Correlation
cor(cars$dist,cars$speed)
```

```{r}
#Plot the spread
plot(x = cars$speed, y = cars$dist, main="Cars Data", xlab = "Speed(mph)", ylab = "Distance(feet)")
```

We can see as speed increases distance is also increasing, we can safely assume that distance is a function of speed.

# Linear Model

```{r}
cars_model <- lm(cars$dist ~ cars$speed)
summary(cars_model)
```

Summary:  R-squared for the model is  .6511, so model explains around 65% of the variation in distance due to speed. Also the standard error is very less compared to the coefficients(around 10 times) which is good for the model.

```{r}
plot(cars$speed, cars$dist, xlab = "Speed (mph)", ylab = "Distance (feet)",main="Speed vsStopping Distance")
abline(cars_model)
```

The regression line will be : 

distance = -17.5791 + 3.9324 * speed

# Residuals

```{r}
summary(residuals(cars_model))
```

The mean is equal to zero, so that looks good.

```{r}
plot(cars_model$residuals ~ cars$speed, xlab='Fitted Values', ylab='Residuals',main="Speed vs Linear Model Residuals")
abline(h=0, lty=3)
```

```{r}
qqnorm(cars_model$residuals)
qqline(cars_model$residuals)
```

Seeing the residual plot, we can see there is constant variability and no pattern. Q-Q plot also looks good with some outliers at the tails.




